Is it time for an NBA expansion?

### 2024-04-20 paper/paper.qmd
References Update

library(tidyverse)
library(knitr)
library(readr)
library(modelsummary)
library(tinytex)
library(lubridate)
```

@@

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

library(tidyverse)
library(knitr)
library(modelsummary)
library(tinytex)
library(lubridate)
library(bibtex)
```

@@

@gebru2021datasheets

@@

@@

@@
